p-Adic Stability In Linear Algebra

### 2015-05-22 examples/stability.tex
US letter format
ACM remarks

\documentclass{sig-alternate}
\usepackage[utf8]{inputenc}

@@

\title{p-adic stability in linear algebra}

\numberofauthors{3}
\author{
\alignauthor Xavier Caruso\\
  \affaddr{Universit\'e Rennes 1}\\
  \email{\normalsize \textsf{xavier.caruso@normalesup.org}}
\alignauthor David Roe \\
  \affaddr{University of British Columbia}\\
  \email{\normalsize \textsf{roed.math@gmail.com}}
\alignauthor Tristan Vaccon\\
  \affaddr{Universit\'e Rennes 1}\\
  \email{\normalsize \textsf{tristan.vaccon@univ-rennes1.fr}}
}

@@

\category{I.1.2}{Computing Methodologies}{Symbolic and Algebraic Manipulation -- \emph{Algebraic Algorithms}}
\terms{Algorithms, Theory}
\keywords{$p$-adic precision, linear algebra, ultrametric analysis}

@@

\noindent
{\bf Description and tangent space.}
Let $V$ denote a fixed subspace of $E$ of dimension $d$. The 
Grassmannian $\Grass(E,d)$ can be viewed as the quotient of the set 
of linear embeddings $f: V \hookrightarrow E$ modulo the action (by 
precomposition) of $\GL(V)$: the mapping $f$ represents its image 
$f(V)$. It follows from this description that the tangent space of 
$\Grass(E,d)$ is canonically isomorphic to $$\Hom(V, E) / \End(V) 
\simeq \Hom(V, E/V).$$

@@

%\vspace{-1ex}\noindent\hrulefill

%\medskip

@@

\bibliographystyle{plain}
\bibliography{../roebib/Biblio,extras}

>>>>

\documentclass{sig-alternate-2013}

\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}

\usepackage[utf8]{inputenc}

@@

\title{p-Adic Stability In Linear Algebra}

\numberofauthors{3}
\author{
\alignauthor Xavier Caruso\\
  \affaddr{Universit\'e Rennes 1}\\
  \affaddr{\textsf{xavier.caruso@normalesup.org}}
\alignauthor David Roe \\
  \affaddr{University of British Columbia}\\
  \affaddr{\textsf{roed.math@gmail.com}}
\alignauthor Tristan Vaccon\\
  \affaddr{Universit\'e Rennes 1}\\
  \affaddr{\textsf{tristan.vaccon@univ-rennes1.fr}}
}

@@

\category{I.1.2}{Computing Methodologies}{Symbolic and Algebraic Manipulation -- \emph{Algebraic Algorithms}}
\terms{Algorithms, Theory}
\keywords{$p$-adic precision; linear algebra; ultrametric analysis}

@@

\noindent
{\bf Description and tangent space.}
Let $V$ denote a fixed subspace of $E$ of dimension $d$. The 
Grassmannian $\Grass(E,d)$ can be viewed as the quotient of the set 
of linear embeddings $f: V \hookrightarrow E$ modulo the action (by 
precomposition) of $\GL(V)$: the mapping $f$ represents its image 
$f(V)$. It follows from this description that the tangent space of 
$\Grass(E,d)$ is canonically isomorphic to $\Hom(V, E) / \End(V)$,
which is $\Hom(V, E/V)$.

@@

@@

{\raggedright
\bibliographystyle{plain}
\bibliography{../roebib/Biblio,extras}
}
